Marriage Data analysis

### 2024-09-27 paper/paper.qmd
More edits on discussion

## Shelter Utilization Analysis
The Utilization Rate as being calculated as:
$$\text{Utilization Rate} = \left( \frac{\text{Number of Occupancy}}{\text{Number of Capacity}} \right) \times 100\%$$
From @fig-shelter-utilization, it's the utilization rate in Toronto remains the lowest over 4 years almost all the time compared to other cities, but still in a relativly high number. This suggest that shelter servise croass all four cities are not over-inveseting, their servise are actually helping the hoemelss population since alot of people are using them. There is a significant decrease in utilization rate from Fall 2019 to Summer 2020, despite the increase in occupation number as sugessted in @fig-shelter-over-time. This incicated that more shelter are timely provided, the goverment are providing larger amount of shelter than usual during pandemic. This actully can be visulized in @fig-shelter-provided, espcially in the case for Scarborugh, there is a noticibke peak at very end of 2019 and start of 2020.
```{r}
#| label: fig-shelter-utilization
#| fig-cap: Yearly change in Utilization Rate Average on All Shelters by City (2017-2020)
#| echo: false
#| message: false
#| warning: false

@@

## Over Capacity Cases
The relashipship between Occupancy and Capcity over this four year (see @fig-occupancy-capacity-relashionship) are revealling cases where more tha expectted people are living in the shelter, as we dicusssued in Data section @sec-data. These cases where capacity is exceeded (when $occupancy > capacity$) are importent when considering improvement shelter system improvement. By further invisted to the dataset, we are ablt to identify cases are actually happens to Families sector in Toronto (see @fig-overcapacity). And all other sector didn't expereince overcorwaaed shelter. Think incidate the quility of shleter servise is good at most case. Families sector are expereiceing overcraodded shelter does not implies the shelter system's fault, it is likely that families with children are assigned to a room with bed/mat that is smaller compared to thier family size. 2 children are able to sleep in one bed, this does not seems like a proalem. For example, a family of five with small children, can elect to be accommodated in a room with four beds, as stated in explanamtion of "CAPACITY" feature in the Portal @Shelter.

@@

Based on the information said in @sec-results, particularly  @fig-shelter-utilization, we can see the selter servise system in the CIty of Toronto are indded good structured. The untillization rate is usually in the 90% - 100% region. Suggesting that what being provided are well-used and supportivie to the homeless community.

## COVID-19 Effect

Thorugh looking at the plot @fig-shelter-over-time, the ococupanny of shleters are at the highest around WInter 2019 to the begining of 2020. The pendenmic is indeed infecting the homeless population across four cities. Government actual in react to the outbreak of COVID-19, in intend to support homeless population are represnted on @fig-shelter-provided, with higher capacities of living nessecities provided. Thorugh higher capaciticies of existing shelter,s or adding in new shelters.

@@

COVID-19 is inded empacting on homeless populations, and the effor of mainting thier living needs is a continuse effort even 5 years after the outbreak. This data contains evidence for govemetn support during the pendemic, but is not inclusive enought to evluated on their performance on shelter servises. This defeinlty reqire more rigours research. And it's also not enought to say about what is the govement' support now, since this data only untill 2020. ALso, the increase untillization rate during covid outbreak could be the case that more people are facing more severe peoeblems so that not even make it to the shelter. 
Understanidng the well-velopneness and imparotance of support networks among people experiencing homelessness is sessential. A more cirtical proalblem comes along it how should the supporte being delievered. A good way to to support while ensuring not to disrupt them, for instance by avoiding practices that displace or isolate people from their communities such as moving people to shelters located far from their usual supports @boucher2022they. This is defienlt a long journey to go.

>>>>

## Shelter Utilization Analysis
The Utilization Rate as being calculated as:
$$\text{Utilization Rate} = \left( \frac{\text{Number of Occupancy}}{\text{Number of Capacity}} \right) \times 100\%$$
As shown in @fig-shelter-utilization, Toronto almost consistently has the lowest utilization rate compared to the other cities over four years, although the rates remain relatively high. This suggests that shelter services are well-used and not over-invested, meaning that the shelters are indeed serving the homeless population effectively. Despite an increase in occupancy around the end of 2019, utilization rates decreased during this period, likely due to an increase in available shelter spaces provided during the COVID-19 pandemic, suggested in @fig-shelter-over-time. This incicated that more shelter are timely provided, the goverment are providing larger amount of shelter than usual during pandemic. This is particularly evident in Scarborough, where a sharp increase in shelter capacity is visible at the end of 2019 and the start of 2020. Refers to @fig-shelter-provided to observe more capacity changes in shelters over time.
```{r}
#| label: fig-shelter-utilization
#| fig-cap: Yearly change in Utilization Rate Average on All Shelters by City (2017-2020)
#| echo: false
#| message: false
#| warning: false

@@

## Over Capacity Cases
The relationship between occupancy and capacity over the four years (@fig-occupancy-capacity-relashionship) reveals instances where shelter capacity was exceeded, as we discussed in the Data section (@sec-data). These cases where capacity is exceeded (when $occupancy > capacity$) are important to study when considering improvement shelter system improvement. By further investigation of the data, these overcrowded cases are primarily observed in the Families sector in Toronto (see @fig-overcapacity). Other sectors did not experience overcapacity, indicating that the shelter services were generally adequate. The possible overcrowding experience that happens to the Families sector may not necessarily reflect poor shelter conditions, as it could result from families being assigned to rooms with slightly fewer beds than their family size would suggest. For example, children might share beds (@Shelter), which does not indicate a systemic issue in shelter management.

@@

Based on the findings, particularly from the utilization rate data @fig-shelter-utilization, the shelter service system in the City of Toronto appears to be well-structured. Utilization rates consistently fall within the 90%-100% range, indicating that shelters are effectively supporting the homeless population.

## COVID-19 Impact

The occupancy of shelters reached its peak around winter 2019 to early 2020, as seen in @fig-shelter-over-time. This increase is likely linked to the COVID-19 pandemic, as shelters saw heightened demand. After this peak, occupancy dropped significantly. Suggesting the efforts by local governments to provide additional resources during the pandemic. The government intention to support homeless population is presented by higher capacities of living resources provided (see @fig-shelter-provided). These might be through higher capacities of existing shelters or adding in new shelters.

@@

COVID-19 has significantly impacted homeless populations, and the effort to meet their needs continues even five years after the outbreak. This data provides evidence of government support during the pandemic, but it is not enough to evaluate the effectiveness of shelter services and other government support for people living in homelessness. More rigorous research is required. The decreased utilization rate during the COVID outbreak may indicate that more individuals are experiencing severe challenges, preventing them from accessing shelters. Furthermore, it is insufficient to comment on the current state of government support since this data only goes up to 2020.

Understanding the development and importance of support services among people experiencing homelessness is essential. Moreover, a critical issue is how this support should be delivered. It is important to provide assistance without disrupting individuals' lives, for instance, by avoiding practices that displace or isolate them from their communities, such as relocating them to shelters far from their usual support systems (@boucher2022they). This is a long journey to go.
